Cores from kicks: inferring the gravitational recoil history of SMBHs in elliptical galaxies.

### 2024-06-04 papers/paper-corekick/paper-corekick.tex
Add Max beta plot to paper

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{anisotropy_profiles_std_log}
    \caption{
        \drafting{\textbf{Max contribution} Put here for now, a better spot elsewhere? Also need to update caption and include in text.}
        Stellar velocity anisotropy parameter $\beta$ as a function of radius for the galaxy mergers with kick velocities between $0\,\kmps$ and $2000\,\kmps$. 
        The stellar particles are divided into 20 logarithmic bins between $0.1\,\mathrm{kpc}$ and $20\,\mathrm{kpc}$.
        The dotted horizontal line indicates $\beta=0$. 
    }
    \label{fig:beta}
\end{figure}
